---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# polydar

<!-- badges: start -->
<!-- badges: end -->

A very raw port of [polylidar](https://github.com/JeremyBYU/polylidar) to try
building an R package with it. 

What I did: 

* clone polylidar
* cp polylidar/polylidar -R polydar/
* cp polylidar/examples polydar/examples
* mv polydar/polylidar polydar/src
* create polydar/Makevars
* cp polydar/examples/cpp/simple-2d.cpp polydar/src/simple-2d-polydar.cpp

and modified that to call what was main from R as `IntegerVector polydar`. 

Set up all the Rcpp and roxygen stuffs - you need `usethis::use_rcpp()` and you need to ensure roxygen is applied when you build i.e. *check 'Install and restart' for roxygen*. 

WIP

## TODO

- [ ] convert to headers usage
- [x] input data from R
- [x] input configuration from R
- [ ] extract polygons and triangles
- [ ] explore configuration and examples

## Not a proper R package yet

Still doing naughty stuff so beware. 

```
R CMD check results ────────────────────────────────────── polydar 0.0.1 ────
Duration: 45.1s

> checking if this is a source package ... WARNING
  Subdirectory ‘src’ contains:
    glue.hpp
  These are unlikely file names for src files.

> checking Rd metadata ... WARNING
  Rd files with duplicated alias 'polydar':
    ‘polydar-package.Rd’ ‘polydar.Rd’

> checking for GNU extensions in Makefiles ... WARNING
  Found the following file(s) containing GNU extensions:
    examples/cpp/Makefile
  Portable Makefiles do not use GNU extensions such as +=, :=, $(shell),
  $(wildcard), ifeq ... endif, .NOTPARALLEL See section ‘Writing portable
  packages’ in the ‘Writing R Extensions’ manual.

> checking top-level files ... NOTE
  Non-standard file/directory found at top level:
    ‘examples’

> checking pragmas in C/C++ headers and code ... NOTE
  Files which contain pragma(s) suppressing diagnostics:
    ‘src/include/parallel_hashmap/phmap.h’
    ‘src/include/parallel_hashmap/phmap_bits.h’

> checking compiled code ... NOTE
  File ‘polydar/libs/polydar.so’:
    Found ‘_ZSt4cerr’, possibly from ‘std::cerr’ (C++)
      Object: ‘polylidar.o’
    Found ‘_ZSt4cout’, possibly from ‘std::cout’ (C++)
      Objects: ‘polylidar.o’, ‘simple-2d-polydar.o’
  
  Compiled code should not call entry points which might terminate R nor
  write to stdout/stderr instead of to the console, nor use Fortran I/O
  nor system RNGs.
  
  See ‘Writing portable packages’ in the ‘Writing R Extensions’ manual.

0 errors ✓ | 3 warnings x | 3 notes x
Error: R CMD check found WARNINGs
Execution halted

Exited with status 1.
```


## Usage

None yet. 

All it does is run the simple2d example, with input data option, config optional: 

```{r simple}
polydar:::polydar()

#> Simple C++ Example of Polylidar
#> Polylidar took 0 milliseconds processing a 5 point cloud
#> Point indices of Polygon Shell: [3,0,1,2]

#> Detailed timings in milliseconds:
#> Delaunay Triangulation: 0.01; Mesh Extraction: 0.00; Polygon Extraction: 0.01
```


This is starting to show a bit more interesting stuff: 

```{r data}
xy <- matrix(unlist(quakes), ncol = 2L)
polydar:::polydar(xy)


polydar::polydar(c(quakes$long, quakes$lat))
```

```
Simple C++ Example of Polylidar
Polylidar took 1 milliseconds processing a 1000 point cloud
Point indices of Polygon Shell: [662,619,837,601,828,973,954,661,692,539,717,667,674,874,638,598,847,799,953,921,755,618,816,732,805,873,640,781,604,649,950,562,745,830,627,564,504,783,677,922,959,648,853,594,521,964,691,612,877,576,901,505,663,510,818,751,744,586,917,688,589,770,690,992,531,941,753,655,558,925,867,913,879,798,508,650,932,889,773,791,957,936,826,536,945,827,893,549,578,754,694]
[699,589,645,818,538,809,690]
[666,675,679,523,659]
[668,672,800,991,673,669,861,557,942,725,985,847,923,710]
[929,700,675]
[872,661,522]
[802,737,551,704,804,741,681,897,872]
[764,587,708]
[597,762,951,950]
[553,709,951]
[944,554,871]
[296,253,125,133,190]
[133,457,432,362]
[362,443,155]
[390,493,327,58]
[312,152,43,293,418,60,254,389,3,121,194,258,384,285,379,233,460,340,182,454,398,70,360,178,314,26]
[236,164,38,251,76,309,163,279,15,159,62,84,453,455,244,114,305,421,95,297,356,342,355,492]
[211,17,54,444,368,56,395,201,138,82,57,129,311,324,238,167,411,185,94,410,353,198,287,286,187,352,408,189,250,205,68,274,256,497]

Detailed timings in milliseconds:
Delaunay Triangulation: 0.95; Mesh Extraction: 0.19; Polygon Extraction: 0.20
[1] 0
```


---

## Code of Conduct
  
Please note that the polydar project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
